Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-09 manuscript-figures.Rmd
update manuscript figures
so far only finished the first 3*. need to fix figure 5 (Topt heatmap). there's an issue where the contours are extending to the infinite sigmaH band when they're not supposed to. likely caused by choosing the wrong value for sigmaH proxies

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp) #nec
library(reshape2) #nec
library(cowplot)
library(viridis)
library(RColorBrewer) #nec
library(MetBrewer)
library(here)
library(lemon)  #nec
library(zplyr) # only needed for placing text using absolute coordinates in contact comparison figure

@@

# Load in necessary functions and files---------------------------------------------------
# Functions for computing equilibrium quantities:
#  mosquito abundance (compute.V0), basic reproduction number (compute.R0)
source("code/output-functions.R")
```

```{r load-data, include=FALSE}
# Run analysis scripts to obtain data for plotting------------------------------
source("code/get-mosquito-traits.R")
source("code/get-analysis-dfs.R")

# Load data files and configure for plotting------------------------------------

## Vector trait thermal performance curves
VecParms <- read_csv("results/VectorTraits.csv", show_col_types = FALSE)

## Compute mosquito thermal tolerance range (minimum and maximum)
MosqThermRange_df <- VecParms %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
    system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  )) %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()

## All outputs
  AllOutputs <- read_csv("results/AllOutputs.csv", show_col_types = FALSE)

  # Title names for each mosquito+pathogen combination (NB: to be added to get-analysis-dfs.R)
  AllOutputs <- AllOutputs %>%
    mutate(system_label = case_when(
      system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
      system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
      system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
      system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
      system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
    ))

@@

## Set up plot dataframe
MosqThermTraits_df <- VecParms %>%
  ## Set up plot dataframe
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Select relevant traits and parameters
  select(
    Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP
  ) %>%
  # Turn all columns except Temperature and system_ID (Mosquito sp. + parasite sp.) into
  # 'variables'
  melt(id = c("Temperature", "system_ID")) %>%
  group_by(Temperature, system_ID)

@@

  # color:
  scale_color_manual(
    name = "System:",
    values = met.brewer("Egypt", 5, direction = -1),
    labels = function(x) {
      case_when(
        x == "Aedes aegypti+ZIKV" ~ "*Ae. aegypti* and ZIKV",
        x == "Aedes aegypti+DENV" ~ "*Aedes aegypti* and DENV",
        x == "Aedes albopictus+DENV" ~ "*Aedes albopictus* and DENV",
        x == "Anopheles spp.+P.fal." ~ "*Anopheles* spp. and *Plasmodium falciparum*",
        x == "Culex quinquefasciatus+WNV" ~ "*Culex quinquefasciatus* and WNV"
      )
    }
  ) +

@@

  R0_df <- AllOutputs %>%
    # To set num. of curves, change "length.out" to be the number of curves you want
    filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 21)]) %>%
    # Just consider one finite value of sigmaH and the Ross-Macdonald model
    filter(sigmaH == 100 | is.infinite(sigmaH)) %>%
    # Group by curve_ID and system_ID
    group_by(Model, KH, system_ID) %>%
    # Normalize R0 for each curve_ID x system_ID combination, so that the maximum is always at one
    mutate(norm_R0 = R0 / max(R0)) %>%
    # Restrict temperatures to where R0 is positive
    filter(norm_R0 > 0) %>%
    arrange(system_ID, sigmaH, Temperature)

  ## PLOTTING ##
  R0_plot <- R0_df %>%
    # x = Temperature, y = normalized R0
    # grouped by K_H value
    ggplot(mapping = aes(
      x = Temperature,
      y = norm_R0,
      group = KH
    )) +

    # path of R0 as a function of temperature (finite sigmaH):
    geom_path(
      data = filter(R0_df, sigmaH == 100),
      aes(colour = KH, linetype = "finite")
    ) +
    # path of R0 as a function of temperature (infinite sigmaH):
    geom_path(
      data = filter(R0_df, sigmaH == Inf),
      aes(linetype = "infinite", colour = "black"),
      colour = "black",
      lwd = 1.5
    ) +

    # x-axis:
    scale_x_continuous(
      name = "Temperature (°C)",
      expand = c(0, 0),
      limits = c(15, 35)
    ) +
    # y-axis:
    scale_y_continuous(
      name = TeX("Normalized $R_0$"),
      expand = c(0, .05)
    ) +

    # color: scaled log10, color-blind friendly
    scale_color_viridis(
      name = "Vertebrate host population\ndensity (ind/ha)",
      trans = "log10",
      breaks = 10^seq(-2, 4),
      labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
      option = "plasma"
    ) +

    # linetype:
    scale_linetype_manual(
      name = "Biting tolerance\n(bites per host per day)",
      breaks = c("finite", "infinite"),
      labels = unname(c(TeX("100 (Chitnis)"), TeX("$\\infty$ (Ross-Macdonald)"))),
      values = c("solid", "22")
    ) +

    # legend
    guides(
      color = guide_colourbar(
        title.position = "top",
        nrow = 1,
        barwidth = 12,
        show.limits = TRUE,
        direction = "horizontal"
      ),
      linetype = guide_legend(
        title.position = "top",
        nrow = 2,
        keywidth = 4,
        direction = "vertical"
      )
    ) +

    # theme options:
    theme_minimal_vgrid(11) +
    theme(
      legend.box = "vertical",
      legend.margin = margin(),
      legend.title = element_text(size = 10),
      legend.text = element_text(
        size = 10,
        hjust = 0
      ),
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # move legend into lower right-hand corner
  shift_legend(R0_plot)
```

@@

  Toptalt_df <- ThermPathChars %>%
    ungroup() %>%
    distinct() %>%
    # Arrange along the plotting variables
    arrange(system_label, sigmaH_proxy, KH, Topt)

  # add many proxy sigmaH points at infinity to make the values easier to see there
  temp <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.25 * infinite_divide, infinite_skew))
    ))
  temp2 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.15 * infinite_divide, infinite_skew))
    ))
  temp3 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.05 * infinite_divide, infinite_skew))
    ))
  temp4 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.3 * infinite_divide, infinite_skew))
    ))
  temp5 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.2 * infinite_divide, infinite_skew))
    ))
  temp6 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(1.1 * infinite_divide, infinite_skew))
    ))
  temp7 <- filter(Toptalt_df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
      mean(c(infinite_divide, infinite_skew))
    ))

  Toptalt_df <- add_row(Toptalt_df, temp)
  Toptalt_df <- add_row(Toptalt_df, temp2)
  Toptalt_df <- add_row(Toptalt_df, temp3)
  Toptalt_df <- add_row(Toptalt_df, temp4)
  Toptalt_df <- add_row(Toptalt_df, temp5)
  Toptalt_df <- add_row(Toptalt_df, temp6)
  Toptalt_df <- add_row(Toptalt_df, temp7) %>%
    arrange(sigmaH_proxy) %>%
    distinct()

  Topt_breaks <- seq(21, 31, by = 1)

  Toptalt_plots <- Toptalt_df %>%
    ## Set up plot ##
    # x = biting tolerance (with a point at infinity),
    # y = vertebrate host population density,
    # color = transmission thermal optimum
    ggplot(aes(x = KH, y = sigmaH_proxy)) +

    # Topt for FINITE sigmaH:
    geom_contour_filled(
      data = filter(Toptalt_df, sigmaH_proxy < infinite_divide**0.98),
      aes(z = Topt),
      breaks = Topt_breaks
    ) +

    # Topt for INFINITE sigmaH:
    geom_contour_filled(
      data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.02),
      aes(z = Topt),
      size = 1,
      breaks = Topt_breaks
    ) +

    # R0 = 1 contour:
    geom_contour(aes(z = R0opt, colour = "R0=1"), breaks = c(1), size = 1) +

    # fill:
    scale_fill_manual(
      name = "Transmission thermal optimum (°C)",
      values = met.brewer("Johnson",
        n = length(Topt_breaks),
        direction = -1
      )
    ) +

    # color:
    scale_colour_manual(
      name = "",
      labels = c("R0=1" = unname(TeX("$R_0=1$"))),
      values = c("black"),
      guide = guide_legend(
        order = 1,
        keyheight = unit(1, "cm"),
        override.aes = list(size = 6)
      )
    ) +

    # theme options:
    theme_minimal(11) +
    theme(
      legend.box = "vertical",
      legend.position = "bottom",
      legend.margin = margin(0, 0, 0, 0),
      legend.title = element_text(size = 10),
      legend.direction = "horizontal",
      legend.justification = "left",
      axis.title.x = element_text(hjust = 0.5),
      strip.text = ggtext::element_markdown(
        size = 11,
        hjust = 0,
        padding = margin(0, 0, 0, 0),
        margin = margin(1, 1, 1, 1)
      )
    )

  # Plot
  shift_legend(Toptalt_plots)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp) #nec
library(reshape2) #nec
library(cowplot) #nec
library(viridis) #nec
library(RColorBrewer) #nec
library(MetBrewer) #nec
library(here)
library(lemon)  #nec
library(zplyr) # from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contact comparison figure

@@

# Load in necessary functions and files ----------------------------------------
# Functions for computing equilibrium quantities:
#  mosquito abundance (compute.V0), basic reproduction number (compute.R0)
# source("code/output-functions.R")

# Helper function: add a "point at infinity" for plotting when sigmaH is infinite
inf_skew_func <- function(df, n_rows_to_add) {
  # Value of sigmaH to replace 'Inf' with for plotting
  infinite_skew <- 10^3 + 2500

  # Get the largest value of log10(sigmaH)
  max_log10sigmaH <- filter(df, is.finite(sigmaH)) %>%
    select(sigmaH) %>%
    max() %>%
    log10()

  # add a second proxy sigmaH point at infinity to make the values easier to see there
  temp <- filter(df, is.infinite(sigmaH)) %>%
    mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
  # Create a proxy sigmaH variable that replaces Inf with infinite_skew
  df <- mutate(df, sigmaH_proxy = ifelse(is.finite(sigmaH),
                                         sigmaH, infinite_skew
  ))

  for (i in 1:n_rows_to_add) {
    bump_val <- 1+0.05*(i-1)
    temp <- filter(df, is.infinite(sigmaH)) %>%
      mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                                   mean(c(bump_val * infinite_divide, infinite_skew))
      ))
    df <- add_row(df, temp) %>% distinct()
    }

  return(df)

}

```{r load-data, include=FALSE}
# Run analysis scripts to obtain data for plotting -----------------------------

data.in.transform <- read_rds("data/clean/TPC_param_samples.rds")
# Define temperature range of study
Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301

# Thin sample size
thin_size <- 1000 # full = 1000, thin = 100

plot_bool = FALSE
source("code/trait-transform.R")
# Host density vector: Number of values to include to consider for vertebrate host density
KH_vec_length <- 300 # full = 300, thin = 20

# Biting tolerance vector: Number of values to consider for biting tolerance
sigmaH_vec_length <- 300 # full = 300, thin = 20

source("code/trait-variation.R")

# Load output data -------------------------------------------------------------

# R0 data
data.R0 <- read_rds("results/R0_vals.rds")
# Topt data
data.Topt <- read_rds("results/Topt_vals.rds")
# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds")

# Configure data sets for plotting ---------------------------------------------

## Get mean values of vector traits across samples
mean.Vec <- data.Vec %>% 
  select(-c(mosquito_species, pathogen, muL, etaL)) %>% 
  pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
  group_by(system_ID, Temperature, variable) %>% 
  summarise(mean = mean(value), .groups = "keep") %>% 
  ungroup() %>% 
  pivot_wider(names_from = "variable", values_from = "mean") %>% 
  mutate(etaL = rhoL / (deltaL + eps)) %>%
  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
  mutate(muL = etaL - rhoL) %>%
  mutate(V0 = ifelse( sigmaV_f * deltaL < (1 / lf),
                      0,
                      KL * rhoL * lf * (1 - 1 / (lf * sigmaV_f * deltaL))))

## Compute mosquito thermal tolerance range (minimum and maximum)
MosqThermRange_df <- mean.Vec %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  )) %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()

# Title names for each mosquito+pathogen combination (NB: to be added to get-analysis-dfs.R)
data.R0 <- data.R0 %>%
  ungroup() %>% 
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  ))

@@

## Set up plot dataframe
MosqThermTraits_df <- mean.Vec %>%
  ## Set up plot dataframe
  # Mortality rate
  mutate(muV = 1/lf) %>% 
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Select relevant traits and parameters
  select(
    Temperature, system_ID, lambdaV, sigmaV, betaV, lf, P_EIP
  ) %>%
  # Turn all columns except Temperature and system_ID (Mosquito sp. + parasite sp.) into
  # 'variables'
  melt(id = c("Temperature", "system_ID")) %>%
  group_by(Temperature, system_ID)

@@

  # color:
  scale_color_manual(
    name = "System:",
    values = met.brewer("Egypt", 5, direction = -1),
    labels = function(x) {
      case_when(
        x == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
        x == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
        x == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
        x == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
        x == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
      )
    }
  ) +

@@

# R0 as a function of temperature, seperate curves across values of KH and sigmaH

# Plot R0 vs. temperature curves. One plot for each system
# One curve for Ross-Macdonald, a few for Chitnis

# x-axes = temperature
# y-axes = R0 (normalized so that max(R0) = 1)
# plots = one for each mosquito+pathogen combination, "system_ID"
# curve 1 = Ross-Macdonald R0 (shape doesn't depend on KH)
# curves  = Chitnis dynamic R0,
#   - colour = value of KH. place it on a color scale in the bottom right corner
newKH_vals <- unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]

data.R0_norm <- data.R0 %>% 
  filter(KH %in% newKH_vals) %>% 
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize variables to have a maximum of 1
  group_by(system_ID, Model, sigmaH, KH) %>% 
  # mutate(mean_norm = mean / max(mean)) %>% 
  mutate(median_norm = median / max(median)) %>%
  # mutate(highHCI_norm = highHCI / max(median)) %>% 
  # mutate(lowHCI_norm = lowHCI / max(median)) %>% 
  arrange(system_ID, sigmaH, KH, Temperature, mean_norm)

R0_plot <- ggplot(mapping = aes(x = Temperature, group = KH)) +
  # path of mean, normalized R0 as a function of temperature (finite sigmaH):
  geom_path(
    data = filter(data.R0_norm, sigmaH == 100),
    aes(y = median_norm, colour = KH, linetype = "finite"),
    lwd = 1
  ) +
  # path of mean, normalized R0 as a function of temperature (infinite sigmaH):
  geom_path(
    data = filter(data.R0_norm, sigmaH == Inf),
    aes(y = median_norm, linetype = "infinite", colour = "black"),
    colour = "black",
    lwd = 1.5
  ) +
  # # 89% HCI of R0 TPC curves
  # geom_ribbon(
  #   data = filter(data.R0_norm, sigmaH == 100),
  #   aes(ymin = lowHCI_norm, ymax = highHCI_norm, fill = KH),
  #   alpha = 0.1
  # ) +
  # x-axis:
  scale_x_continuous(
    name = "Temperature (C)",
    expand = c(0, 0),
    limits = c(14, 34)
  ) +
  # y-axis:
  scale_y_continuous(
    name = TeX("Normalized $R_0$"),
    expand = c(0, .05)
  ) +
  # color: scaled log10, color-blind friendly
  scale_color_viridis(
    name = "Vertebrate host population\ndensity (ind/ha)",
    trans = "log10",
    breaks = 10^seq(-2, 4),
    labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
    option = "plasma"
  ) +
  # fill: scaled log10, color-blind friendly
  scale_fill_viridis(
    name = "Vertebrate host population\ndensity (ind/ha)",
    trans = "log10",
    breaks = 10^seq(-2, 4),
    labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
    option = "plasma"
  ) +
  # linetype:
  scale_linetype_manual(
    name = "Biting tolerance\n(bites per host per day)",
    breaks = c("finite", "infinite"),
    labels = unname(c(TeX("100 (Chitnis)"), TeX("$\\infty$ (Ross-Macdonald)"))),
    values = c("solid", "22")
  ) +
  # faceting:
  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
  # legend
  guides(
    color = guide_colourbar(
      title.position = "top",
      nrow = 1,
      barwidth = 12,
      show.limits = TRUE,
      direction = "horizontal"
    ),
    linetype = guide_legend(
      title.position = "top",
      nrow = 2,
      keywidth = 4,
      direction = "vertical"
    )
  ) +
  # theme options:
  theme_minimal_vgrid(16) +
  theme(
    legend.box = "vertical",
    legend.margin = margin(),
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
R0_plot <- shift_legend(R0_plot)

@@

Toptalt_df <- data.Topt %>%
  ungroup() %>%
  distinct() %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, mean) %>% 
  mutate(sigmaH_proxy = sigmaH)

# add many proxy sigmaH points at infinity to make the values easier to see there
Toptalt_df <- inf_skew_func(Toptalt_df, 6)

# Define sigmaH tick breaks and labels
sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), infinite_divide, 10^log10(mean(c(infinite_divide,infinite_skew))))
sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

min_Topt <- floor(min(min(Toptalt_df$mean),min(Toptalt_df$median)))
max_Topt <- ceiling(max(max(Toptalt_df$mean),max(Toptalt_df$median)))
Topt_breaks <- seq(min_Topt, max_Topt, by = 1)

# Plot mean of Topt heat map
Toptalt_plots <- Toptalt_df2 %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # Topt for FINITE sigmaH:
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy < infinite_divide**0.99),
    breaks = Topt_breaks
  ) +
  # Topt for INFINITE sigmaH:
  # take mean of mean to hide variation from artifacts of uncertainty 
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy > infinite_divide**1.01) %>% 
      group_by(system_ID) %>% 
      mutate(mean = mean(mean), .groups = "keep"),
    size = 1,
    breaks = Topt_breaks
  ) +
  # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
  geom_contour(data = filter(data.CT, variable == "CTwidth"),
               aes(y = sigmaH, z = mean, colour = "R0 = 1"), 
               breaks = min(filter(data.CT, variable == "CTwidth", mean > 0)$mean),
               size = 1) +
  # geom_contour(data = data.R0_norm,
  #              aes(y = sigmaH, z = mean, colour = "R0=1"), breaks = c(1), size = 1) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

  # fill:
  scale_fill_manual(
    name = "Transmission\nthermal optimum (°C)",
    values = met.brewer("Johnson",
                        n = length(Topt_breaks),
                        direction = -1
    )
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c("R0=1" = unname(TeX("$R_0=1$"))),
    values = c("black"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(1, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # faceting:
  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0,
    barheight = unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "vertical",
    legend.position = "right",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "vertical",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
Toptalt_plots <- shift_legend(Toptalt_plots)
